Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-20 latex/paper.tex
修改结果与分析与结论

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-20 00:54:19
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime. The heat capacity  could be computed with Eq. \ref{eq:cv} .

@@

The thermal conductivity converged with cutoff MFP very quickly in the curve of 2l2 while a little slower in the others. Besides, the cutoff MFP of 2l1 structure exhibits much difference in the two directions  which maybe due to the diffence of scattering intensity caused by the surface conditions.When the length of the silicene is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious. When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious. The empirical formula of the John A. Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials. Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicene
\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}})
\end{equation}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

@@

To have inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.\ref{eq:kappasum}.

Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq. \ref{eq:cv}. The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$. The average heat capacity of the structures are shown in Table.\ref{tab:table1} . Large difference could be found between the $Cv$ of the structures. The lowest value is $17.26 kJ/m^3/K$ of 8l1 while the highest value of 2l1 could reach $166.7 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.  Almost no difference could be found in the value along zigzag direction and armchair direction. This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high. That means when considering only acoustic phonons the heat capacity is close to constant.

@@

The phonon lifetime
The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures. We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons. Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$). So this process is called Umpack process( U process). And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process. If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance. The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014}.considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.

The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity. The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity. The relation between acoustic phonon lifetime and frequency could be expressed as $\tau=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures. The coefficient k for both direction are displayed in Table.3. The degree of divergence exhibit large anisotropy for the structures. However the difference of lifetime is pretty small when frequency is relatively high. So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.

@@

The anisotropy of phonon velocity has little contribution for the anisotropy of the thermal conductivity. FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures. The group velocity  along the two directions of  2 layers silicene ( include silicene) are exactly the same except for that of 2lr3 structure whose low frequency group velocities are highly anisotropic. Group velocity for the others are all highly anisotropic and it's obvious that the group velocity of armchair direction are all large than that of zigzag. The relation between the group velocity of both direction are contrast with that of the thermal conductivity, which indicate that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects.

@@

To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.
The transmission function can be expressed as
\begin{equation}
  \begin{split}
    \Theta(\omega)= Tr(
    \mathbf{\widetilde{k}}_{a\alpha}
    Im(\mathbf{g}_{\alpha\alpha})
    \mathbf{\widetilde{k}}_{\alpha a}
    \mathbf{G}_{a b}^*\\
    \mathbf{\widetilde{k}}_{b\beta}
    Im(\mathbf{g}_{\beta\beta})
    \mathbf{\widetilde{k}}_{\beta b}
    \mathbf{G}_{b a}
    )
  \end{split}
\end{equation}
where $\mathbf{\widetilde{k}}_{a\alpha}$,$\mathbf{\widetilde{k}}_{\alpha a}$ represents for the interaction between left lead and center region and its transposition,  $\mathbf{\widetilde{k}}_{b\beta}$,$\mathbf{\widetilde{k}}_{\beta b}$ the interaction between center and right lead. $\mathbf{g}$ and $\mathbf{G}$ the retarded Green's function of the leads and center rigion.$Tr$ and $Im$ means trace and imaginary function. Transmission function represents for the number of channels of a given frenquency. The more chanels means larger capability of thermal transportation. The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.

FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions. The y-axis value of each panel is not the same so the transmission is given here only to explain the anisotropy of each strcutre. The steps in the curves are  characterisic of perfection of the structure. Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of Silicene and 2l1 are perfectly stepwise because of the perfect bonding and the absence of disorder.

Similar to the situation of participation ratio, transmission of both directions of Silicene,2l1 are close.Especially that of 2l2 are exactly the same, which is due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair. This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity. The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this may contribute a lot to the anisotropy of the thermal transportation.

@@

By means of non-equilibrium molecular dynamics simulation, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 11.6 W/mK (2l1 structure), and can be as low as 1.2 W/mK (2l2 structure) and the anisotropy can be as high as 57.3\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene has good thermoelectric properties. In the 3-6 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased. The thermal conductivity anisotropy of the multilayer silicene with 10 layers is very small, which is consistent with the bulk Si and monolayer silicene. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-20 20:47:21
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime. The heat capacity  could be computed with Eq.(\ref{eq:cv}) .

@@

The thermal conductivity converged with cutoff MFP very quickly in the curve of 2l2 while a little slower in the others. Besides, the cutoff MFP of 2l1 structure exhibits much difference in the two directions  which maybe due to the diffence of scattering intensity caused by the surface conditions.When the length of the silicene is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious. When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious. The empirical formula of the John A. Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials. Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicene
\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
\end{equation}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

@@

To have a deeper inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).

Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq.(\ref{eq:cv}). The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$. The average heat capacity of the structures are shown in Table.\ref{tab:table1} . Large difference could be found between the $Cv$ of the structures. The lowest value is $17.26 kJ/m^3/K$ of 8l1 while the highest value of 2l1 could reach $166.7 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.  Almost no difference could be found in the value along zigzag direction and armchair direction. This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.

@@

The phonon lifetimes are the main factor of anisotropy in two layer structures while they are less essential in that of structures with more than three layers. When calutating phonon lifetimes, only three-phonon scattering process are considered,which consists of two types of scattering processes, within one of which  two phonons vanish and one phonon be created and the other type is one phonon transform to two phonons. Both of them are possible to have result phonons with q point outside Brillouin boundry, which must be fold back to Brillouin zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$). So this process is called Umpack process( U process). And of cause there exist  situation that none of the three q points outside the Brillouin boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process. If there's no U process the thermal conductivity could be as large as possible, so this process gives the dominent contribution to thermal resistance. The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014} considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value. The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2lh has reverse relation. However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.

@@

While the anisotropy lifetime in two layer structures affects more than that of group velocity, group velocity contributes most of anisotropy in multilayer structures with layers more than three.  FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures. The group velocity  along the two directions of  2 layers silicene ( include silicene) are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic. Group velocity for the others exhibits similar curve and are all highly anisotropic both in low and high frequency range. The group velocity of zigzag direction are all large than that of zigzag. These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in two layer silicene but the reverse for the structures thicker.

@@

Not only group velocity,but also phonon transmission clearly show that  localization of ballistic contribution from long wave phonons dominant the anisotropy of the structures with layers more than three.To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.The transmission function can be expressed as
\begin{equation}
  \begin{split}
    \Theta(\omega)= Tr(
    \mathbf{\widetilde{k}}_{a\alpha}
    Im(\mathbf{g}_{\alpha\alpha})
    \mathbf{\widetilde{k}}_{\alpha a}
    \mathbf{G}_{a b}^*\\
    \mathbf{\widetilde{k}}_{b\beta}
    Im(\mathbf{g}_{\beta\beta})
    \mathbf{\widetilde{k}}_{\beta b}
    \mathbf{G}_{b a}
    )
  \end{split}
\end{equation}
where $\mathbf{\widetilde{k}}_{a\alpha}$,$\mathbf{\widetilde{k}}_{\alpha a}$ represents for the interaction between left lead and center region and its transposition,  $\mathbf{\widetilde{k}}_{b\beta}$,$\mathbf{\widetilde{k}}_{\beta b}$ the interaction between center and right lead. $\mathbf{g}$ and $\mathbf{G}$ the retarded Green's function of the leads and center rigion.$Tr$ and $Im$ means trace and imaginary function. Transmission function represents for the number of channels of a given frenquency. The more chanels means larger capability of thermal transportation. The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions. The y-axis value of each panel is scaled for a more convinient comparison of transmission in the tow directions. The steps in the curves are  characterisic of perfection of the structure. Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of  2l1 is perfectly stepwise because of the perfect bonding and the absence of disorder.Transmission of both directions of 2l1 ,2l2(not show here) and 2lh are close,especially that of 2l2 are exactly the same due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure such as 3l1,4l1,5l1 and 6l1 where transmissioin is larger in zigzag direction than in armchair. This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity. The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this contributes a lot to the anisotropy of the thermal transportation.

@@

By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2lh structure) and the anisotropy can be as high as 41.1\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene 2lh has good thermoelectric properties. In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased. The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
